%!TEX TS-program = xelatex
\documentclass[]{jvcv}

\usepackage{microtype}       % Typography refinements

% Document start
%
\begin{document}

% Header area
\header{Jarred}{Vardy}
       {This CV file is a bootloader! Emulate with QEMU or use a USB to boot.}

%TODO Hyperlink everything that is worth hyperlinking.

%Side-bar
%
\begin{aside}
	\section{Briefly...}\vspace{0.1cm}
	Jarred Vardy
	\hyperref[https://github.com/vardy/]{github.com/vardy}
	Brighton, UK
	\section{Contact...}\vspace{0.1cm}
	\hyperref[mailto:jarred.vardy@gmail.com]{jarred.vardy@gmail.com}
	\hyperref[https://linkedin.com/in/jarred-vardy]{linkedin.com/in/jarred-vardy}
\end{aside}

% About Me
%
\section{About Me}
Full-stack web developer and back-end software engineer.
I focus keenly on efficiency and cleanliness, taking care to have readable, documented code.

As all of my programming knowledge is self-taught and experienced personally, I feel I have a
deeper knowledge of the areas I delve into, having gone through the trial-and-error process.

% Skills
%
\vspace{0.5cm}
\section{Skills}
\subsection{Languages}
More fluently: Java, Python, JavaScript (Node, Vue, In-Browser), LaTeX, HTML, CSS\\
Less fluently: C, Assembly, Crystal, Go, PHP

\vspace{0.1cm}
\subsection{Other}
Soft skills go here.
%TODO speaking and conveying ideas.
%TODO speaking my mind when something doesnt look right
%TODO unit testing, continuous deployment, version control, Docker, DevOps
%TODO unix systems, system architecture, SSH, FTP, deployment
%TODO show these skills again in experience and projects sections.

% Experience
%
\vspace{0.5cm}
\section{Experience}

\subsection{Jobs}
\vspace{0.05cm}

\begin{jobslist}
	\jobentry
		{2019 - Now}
		{Asialion - full-stack web developer}
		{Remote, paid}
		{\begin{itemize}
			\item Produced two fully-featured and functioning web portals, solo.
			\item Utilised the PHP Laravel framework with VueJS on the front-end.
			\item Updated the main website with SEO and increased efficiency by creating a progressive web app architecture, minimising payload size and optimising resource calls.
			\item Solved technical issues in legacy proprietary software to allow for a smoother workflow for employees.
		\end{itemize}}
\end{jobslist}

% Personal Projects
%
\vspace{0.1cm}
\subsection{Personal Projects}
\vspace{0.05cm}

\begin{projectslist}
	\projectentry
		{2017}
		{IB.ai {\normalfont - private Discord bot.}}
		{Team-built, FOSS, Java}
		{\begin{itemize}
			\item Programmed a large portion of the core of the service in Java.
			\item Lead the project in way of design and architecture. Employed Kanban and other project management tools.
			\item Lead DevOps, using Docker and remote server hosts.
			\item Crowd-funded the project.
		\end{itemize}}
\end{projectslist}
%TODO List projects - monetised? Tags! Same as website.

\newpage

% Interests
%
\section{Interests}
%TODO Add interests

% Education
%
\vspace{0.5cm}
\section{Education}

\begin{edulist}
	\eduentry
		{2020 - Now}
		{Bsc. Computer Science}
		{University Bachelor's}
		{Studying Computer Science, majoring in\\
		software engineering and minoring in operating systems.}
	\eduentry
		{2017 - 2018}
		{International Baccalaureate Diploma}
		{High School}
		{Graduated with a score of 37 from St. Joseph's\\
		Institution International}
\end{edulist}

\end{document}